\documentclass{scrartcl}

\usepackage{template}

\begin{document}

\section{README}

\subsection{Pages}

\href{algebra.html}{Algebra} (very incomplete)

\subsection{Disclaimer}

This website is currently written and maintained by one undergraduate student (me).
I feel like everything here is---at least at its core---correct, but obviously I have a very narrow perspective on
mathematics as a whole.
As such, do not blindly believe the material presented here, and if you find any errors, please create a
\href{https://github.com/xtevenx/ugm/issues}{GitHub issue}!

\subsection{Contributing}

Please do! Even just reading and keeping an eye out for errors is greatly appreciated.

Because I am doing this mainly for selfish reasons (see "About" section below), there are currently no guidelines on
how to contribute.
If you are interested in helping out, feel free to create a GitHub issue to discuss.

\subsection{About}

This website was created for two main reasons.

The first is for my own desires to review past course material.
I feel that a semester (in my case, four months) is not enough time properly absorb new material, so I sometimes
revisit courses six months to a year after they're finished.
This way, I can review after spending a couple semesters studying different areas of mathematics, often using these
experiences to gain new insight into the material.

The second is to help out other students who are in a scenario I have often been in: trying to find simple proofs of
theorems, but only getting ones which reference unknown material, or ones which just present a very rough and
unconvincing sketch (or both).
There seems to be a lack of a single good resource for the content between introductory calculus, and graduate school.
That being said, do note that asking the professor is usually the best way to get a clear explanation, but that is not
always possible.

Due to these reasons, an attempt is made to present the proofs on this website in the most elementary manner possible,
or at least only referencing material which has also been covered here.
Because of this, a strong student may find the proofs too verbose, but that is by design: I am not a strong student, so
hopefully this website can help people like me.

\end{document}
